\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{parskip}

\titleformat{\section}{\large\bfseries}{}{0em}{}

\begin{document}

\begin{center}
    {\LARGE \textbf{Teaching Resume}}\\[1ex]
\end{center}

\section*{Summary}
Experienced college professor of mathematics, high school mathematics teacher, and private tutor, with combined 16 years of teaching and tutoring. Seeking evening adjunct teaching (in person), remote and/or On-Line, or evening tutoring position. Experienced in writing curriculum, learning assessment, PowerPoint lectures, interactive lessons, Blackboard, Canvas, PowerSchool, and PowerTeacher. Highly experienced in maintaining instructional websites and interactive white boards.

\section*{Education}
\begin{itemize}[leftmargin=*]
    \item Sep. 2017 -- June 2022: Doctor of Philosophy (Ph.D.) in Mathematics, Temple University, Philadelphia, PA
    \item Sep. 2012 -- June 2016: Master of Arts (M.A.) in Mathematics, Rowan University, Glassboro, NJ
    \item Sep. 2008 -- Sep. 2009: Teacher of Mathematics Certificate, New Jersey Department of Education, Trenton, NJ
    \item Sep. 2003 -- June 2007: Bachelor of Science (B.S.) Electrical \& Computer Engineering, Rutgers University, New Brunswick, NJ
    \item Sep. 1999 -- June 2003: High School Diploma, Pitman High School, Pitman, NJ
\end{itemize}

\section*{Experience}
\subsection*{Sep. 2017 -- June 2022: Teaching Assistant, Temple University}
\begin{itemize}[leftmargin=*]
    \item Graded assessments and graded coordinated course examinations
    \item Provided one-on-one tutoring to undergraduate students
    \item Designed assessments which included midterm examinations and quizzes
    \item Setup course websites using Blackboard and Canvas
    \item Designed course syllabi
    \item Attended coordinated course meetings and provided feedback
    \item Collaborated with professors to improve and implement effective instructional practices
    \item Piloted graduate student teaching experiential learning
    \item Proctored exams
    \item Provided students mentoring through graduate mathematical talks, SIAM talks/events, mentoring on math department graduate projects, and undergraduate math club talks
\end{itemize}

\subsection*{Spring 2017: Adjunct Professor, Rowan University}
\begin{itemize}[leftmargin=*]
    \item Adjunct Professor of instruction for evening Calculus I course
    \item Designed lectures, lecture notes, and interactive lessons
    \item Designed assessments which include examinations, quizzes, and daily assessments
    \item Provided abundant office hours before and after class
    \item Provided ample review sessions for examinations
    \item Provided frequent feedback to students via email communications and communications through Canvas
    \item Graded examinations, quizzes, and daily assessments
    \item Provided feedback on hand graded homework assignments
    \item Maintained and updated Canvas website on a daily basis
    \item Utilized announcement features on Canvas to send course updates
\end{itemize}

\subsection*{Sep. 2009 -- June 2017: High School Mathematics Teacher, Clearview Regional School District}
\begin{itemize}[leftmargin=*]
    \item Certified mathematics teacher for 9th--12th grade
    \item Designed lessons to be interactive and student oriented
    \item Designed and implemented NJ Core Content Standards
    \item Attended district professional development events including NJEA teacher conventions
    \item Attended workshops on implementing ``Accountable Talk'' in the classroom
    \item Attended workshops on incorporating technology into the classroom (TI-84 calculators, Geometer's Sketchpad)
    \item Collaborated with colleagues to design coordinated examinations
    \item Provided night school instruction and home schooling
    \item Co-taught courses with special education teachers to meet student needs
    \item Fulfilled IEP requirements and 504 plans
    \item Designed lessons to accommodate IEPs and 504 plans
    \item Provided after school hours for tutoring and extra help
    \item Participated in extracurricular activities: Mr. Clearview, track/field timer, dance chaperoning, event security
    \item Communicated actively with parents via phone, email, and website
    \item Completed required duties: hall monitor, cafeteria monitor, ISS teacher, NJ standardized test proctor
    \item Participated in student recognition through NHS awards, recommendations, and student-of-the-month selections
    \item Mentored Rowan University education majors by providing feedback, observations, and experiential learning
\end{itemize}

\subsection*{Sep. 2011 -- June 2016: Private Tutor, Gloucester County, NJ}
\begin{itemize}[leftmargin=*]
    \item Provided one-on-one tutoring and instruction to local county students
    \item Coordinated scheduling with parents
    \item Provided hands-on lessons and practice
    \item Discussed with parents their child's progress
    \item Used manipulatives to teach grade school through high school topics
    \item Provided mentoring on goals and career outlook
\end{itemize}

\section*{Teaching}
\textbf{At Temple University}
\begin{itemize}[leftmargin=*]
    \item Spring 2022: Math 1033, Math 1034
    \item Fall 2021: Math 1039, Math 0702
    \item Spring 2021: Math 1041
    \item Fall 2020: Math 1021
    \item Spring 2020: Math 1041
    \item Fall 2019: Math 1041
    \item Summer 2019: Math 1041
    \item Fall 2018: Math 1039
    \item Summer 2018: Math 1041
    \item Spring 2018: Math 0824 (Grader)
    \item Fall 2017: Math 0824 (Grader)
\end{itemize}

\textbf{At Rowan University}
\begin{itemize}[leftmargin=*]
    \item Spring 2017: Calculus I
    \item Fall 2016: Calculus I
\end{itemize}

\textbf{At Clearview Regional High School}
\begin{itemize}[leftmargin=*]
    \item Honors and Advanced Algebra 1
    \item Honors, Advanced, and Basic Geometry
    \item Honors Algebra 2
    \item Honors Calculus I
    \item College Mathematics
\end{itemize}

\section*{Skills}
\begin{itemize}[leftmargin=*]
    \item Microsoft Office: Word, PowerPoint, Excel
    \item LaTeX: Syllabi, Lecture Notes, Beamer Presentations
    \item Geometer’s Sketchpad, TI-84 Calculator
    \item Websites: Canvas, Blackboard
    \item Student tracking: PowerSchool, PowerTeacher
    \item Communication: Email, phone, in-person, group meetings
    \item Lesson Design: Interactive, adaptable, curriculum/assessment
    \item Interactive white boards
\end{itemize}

\section*{Awards}
\begin{itemize}[leftmargin=*]
    \item March 2022: Dissertation Completion Grant
    \item May 2022: Jay Novik Graduate Student Fellowship
    \item Jan. 2019: Temple University Math Department Excellence in Teaching
    \item Nov. 2018: Certificate of Recognition from SIAM
    \item 2015--2016: Rowan University Certificate of Achievement in Mathematics
    \item 2014--2015: Rowan University Certificate of Achievement in Mathematics
\end{itemize}

\section*{Professional Affiliations}
\begin{itemize}[leftmargin=*]
    \item Sep. 2018 -- June 2022: Temple University SIAM Chapter President and Member
    \item Sep. 2018 -- June 2022: SIAM Member and journal subscriber
    \item Sep. 2017 -- June 2022: AMS Member
    \item Sep. 2017 -- June 2022: MAA Member
    \item Sep. 2015 -- June 2017: Pi Mu Epsilon Chapter Member, Rowan University
    \item Sep. 2008 -- June 2017: NJEA Member, Clearview Education Association
    \item Sep. 2006 -- Sep. 2008: IEEE Member and journal subscriber
\end{itemize}

\section*{Languages}
\begin{itemize}[leftmargin=*]
    \item English: Native Language
    \item Spanish: Conversational and Written
\end{itemize}

\section*{Hobbies}
\begin{itemize}[leftmargin=*]
    \item Reading: Neuroscience, mathematics, scifi, history, poetry
    \item Writing: Mathematical articles, poetry, drawing, painting
    \item Personal Fitness: Running, lifting, hiking
    \item Sports: Orioles/Phillies (baseball), Ravens/Eagles (football)
    \item Games: Video and board games
    \item Travel: US and international
    \item Dining: Restaurant hopping
\end{itemize}

\end{document}
